Alexis Roche

### 2021-07-16 cv/cv.tex
Update cv

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Programming:}
\ \\ 
\ \\
\ \\ 
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Languages: C, Python, Matlab, R. \\
{\tiny$\bullet$} Python packages: numpy, scipy, pylab, skimage, opencv, sklearn, pytorch, TensorFlow, keras.\\
{\tiny$\bullet$} C/Python integration via cython.\\
{\tiny$\bullet$} Version control software: git, svn, perforce. \\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6376 citations, h-index: 32, i10-index: 65 (April 2021).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Teaching:}
\ \\ 
\ \\
\  \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Brain morphometry post-graduate lecture (2h), Lausanne: UNIL (2014/16), EPFL (2015/16).\\
{\tiny$\bullet$} Statistical analysis in neuroimaging, INSERM/CNRS continuing education, France (10h/year from 2003 to 2015).\\
\end{minipage}

>>>>

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Computer skills:}
\ \\ 
\ \\
\ \\ 
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} Programming languages: C, Python, Matlab, R. \\
{\tiny$\bullet$} Python packages: numpy, scipy, pylab, skimage, opencv, sklearn, pytorch, tensorflow, keras.\\
{\tiny$\bullet$} C/Python integration via cython.\\
{\tiny$\bullet$} Version control software: git, svn, perforce. \\
{\tiny$\bullet$} Reporting: \LaTeX, MS~Office, OpenOffice, LibreOffice, Google~Docs. \\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications. Full list: \url{http://orcid.org/0000-0002-4821-6893}. \\
{\tiny$\bullet$} Google scholar statistics: 6602 citations, h-index: 33, i10-index: 66 (July 2021).\\
{\tiny$\bullet$} 5 published international patents. 2 ongoing applications.\\
\end{minipage}

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Academic work:}
\ \\ 
\ \\
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
  {\tiny$\bullet$} Post-graduate teaching in computer vision and medical image analysis: about 100~hours (Ecole Centrale Paris, EPFL Lausanne, University of Nice, University of Lausanne, INSERM/CNRS continuing education, \ldots).\ \\
  {\tiny$\bullet$} Long-time scientific journal reviewing experience (IEEE Trans.~Medical Imaging, Medical Image Analysis, NeuroImage, IEEE Trans.~PAMI, IEEE Trans.~Signal Processing, Frontiers in Neuroscience, \ldots).\ \\  
\end{minipage}
